Using SMT engine to generate Symbolic Automata\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2018-01-22 2017-Xudong-SMT/FM-2018-extended.tex
Added some text in the conclusion about BIP architectures

In this paper, we presented an algorithm for generating an open
automaton representing the semantics of an open pNet.
We have also presented our implementation, which comprises two main parts. Firstly, we
compute all the possible open transitions.
The algorithm combines the actions of subnets and
hole behaviors, which are then matched with the
synchronization vectors by the generated
predicate.  Some of the open transitions obtained at this
intermediate step, constructed in a structural manner from all
possible combinations of possible logical predicates, may
contain predicates which do not represent any possible concrete
instantiations. 
Secondly, to get rid of these useless transitions, we use the SMT solver Z3 for checking the
satisfiability of the predicate in each open transition. 
To this end, we encode into Z3 the representations of the action algebra and
the predicates before submitting them to the
Z3 solver. We implemented our algorithm in the VerCors platform and 
tested the algorithm on available examples, such as encoding expressions from various process algebras. Our case-studies show that our encoding
successfully identifies all unsatisfiable open transitions and that
the resulting automata correctly reflect the expected 
movements of the encoded process expressions.

>>>>

In this paper, we presented an algorithm for generating an open
automaton representing the semantics of an open pNet.
We have also presented our implementation, which comprises two main parts. Firstly, we
compute all the possible open transitions.
The algorithm combines the actions of subnets and
hole behaviors, which are then matched with the
synchronization vectors by the generated
predicate.  Some of the open transitions obtained at this
intermediate step, constructed in a structural manner from all
possible combinations of possible logical predicates, may
contain predicates which do not represent any possible concrete
instantiations. 
Secondly, to get rid of these useless transitions, we use the SMT solver Z3 for checking the
satisfiability of the predicate in each open transition. 
To this end, we encode into Z3 the representations of the action algebra and
the predicates before submitting them to the
Z3 solver. We implemented our algorithm in the VerCors platform and 
\noteSB{Is this still relevant or has it been replaced by the Failure Monitor example?}%
\hl{tested the algorithm on available examples, such as encoding expressions from various process algebras}.
%
\noteSB{New text}%
%
\hl{%
%
In this paper, we used an additional running example, based on a BIP
architecture from an earlier nanosatellite case
study~\cite{CubETH-case-study}.  This example shows that
open-automata-based semantics can be instrumental in verifying the
properties enforced by the architectures through an encoding into open
pNets.  This encoding\mdash which we intend to formalise and prove
correct in a separate paper\mdash also opens the way for an extension
of BIP architectures with the transfer of data among variables of
different components.  Indeed, such data transfer can be easily
encoded using the predicates associated to synchronisation vectors in
open pNets.  The encoding of open transitions into SMTlib and the
availability of theories can guide the definition of such an extension.
%
}
%
Our case-studies show that our encoding
successfully identifies \noteSB{Is this, indeed, the case?}\hl{all} unsatisfiable open transitions and that
the resulting automata correctly reflect the expected 
movements of the encoded process expressions.
